Introduction to Analysis \\ Assignment 8

### 2017-12-06 Graduate - Introduction to Analysis I/Assignment 8/assignment.tex
add prob 5.5 to 5.6

%!TEX program = xelate
\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

@@

\problem{5}{Problem 56, Page 129}
\solution{(i)}{
Since $O$ is an open set, let
$$
O = \bigcup_{n=1}^\infty (a_i, b_i)
$$
be its open decomposition, where $\{(a_i, b_i)\}$ are pairwise disjoint. Then since $g$ is absolutely continuous thus continuous, and $g$ is strictly increasing, $g$ maps an open interval to an open interval (in fact, this has been proved in a midterm exam). Hence, for any open interval $(a, b)$, by Corollary 12 we have
$$
\int_{a}^{b}g'(x) = g(b)-g(a) = m(g((a, b))).
$$
By countable addivity of measure and integral,
$$
\int_{O}g' = \sum_{i=1}^{\infty}\int_{a_i}^{b_i}g' = \sum_{i=1}^{\infty}m(g((a_i, b_i))) = m(g(O)).
$$
}
\solution{(ii)}{
We know that the intersection of two open sets is an open set, then by induction we know
$$
m(g(\cap_{i=1}^n O_i)) = \int_{\cap_{i=1}^n O_i}g', ~\forall n > 0.
$$
Let $E = \cap_{i=1}^{\infty}O_i $, then first we have
$$
m(g(E)) = m(g(\cap_{i=1}^{\infty} O_i)) \le m(g(\cap_{i=1}^{n} O_i)) = \int_{\cap_{i=1}^{n} O_i} g', ~\forall n.
$$
The left side of this inequity is independent of $n$, thus
$$
m(g(E)) \le \int_{\cap_{i=1}^{\infty} O_i} g' = \int_{E}g'.
$$
On the other hand, we know
$$
\int_{E} g' \le m(g(E))
$$
by the same arguments. Hence
$$
m(g(E)) = \int_{E}g'.
$$
}
\solution{(iii)}{
In a midterm exam we have proved that a strictly increasing and continuous function maps a null set to a null set, thus $m(g(E)) = 0$. By Theorem 10 we know $g'$ is integrable on $[a, b]$, then 
$$
\int_{E} g' = 0.
$$
}
\solution{(iv)}{
For any measurable subset $A$, by Theorem 11 of Chapter 2, there is a $G_\delta $ set $G \supset A$, and $m(G\setminus A) = 0$. Let $E = G\setminus A$, by (ii) and (iii), we have
$$
m(g(E)) = \int_{E} g', ~m(g(G)) = \int_{G}g'.
$$
Since $E\cap G = \emptyset$, by addivity of measure and integral,
$$
m(g(A)) = m(g(E)) + m(g(G)) = \int_{E\cup G}g' = \int_{A}g'.
$$
}
\solution{(v)}{

@@

\problem{6}{Problem 59, Page 129}

>>>>

\input{structure.tex}
\usepackage{epstopdf}
\usepackage{graphics}
\usepackage{subfig}
\usepackage{listings}
\lstset{
  breaklines=true,
  xleftmargin=25pt,
  xrightmargin=25pt,
  aboveskip=0pt,
  belowskip=10pt,
  basicstyle=\ttfamily,
  showstringspaces=false,
  frame=ltrb,
  tabsize=4,
  numbers=left,
  numberstyle=\small,
  numbersep=8pt,
  morekeywords={*, factorial, sum, erlang},
  keywordstyle=\color{blue!70}, commentstyle=\color{red!50!green!50!blue!50},
}
\DeclareGraphicsExtensions{.eps,.ps,.jpg,.bmp}

@@

\problem{5}{Problem 56, Page 129}
\solution{(i)}{
Since $O$ is an open set, let
$$
O = \bigcup_{n=1}^\infty (a_i, b_i)
$$
be its open decomposition, where $\{(a_i, b_i)\}$ are pairwise disjoint. Then since $g$ is absolutely continuous thus continuous, and $g$ is strictly increasing, $g$ maps an open interval to an open interval (in fact, this has been proved in a midterm exam). Hence, for any open interval $(a, b)$, by Corollary 12 we have
$$
\int_{a}^{b}g'(x) = g(b)-g(a) = m(g((a, b))).
$$
By countable addivity of measure and integral,
$$
\int_{O}g' = \sum_{i=1}^{\infty}\int_{a_i}^{b_i}g' = \sum_{i=1}^{\infty}m(g((a_i, b_i))) = m(g(O)).
$$
}
\solution{(ii)}{
We know that the intersection of two open sets is an open set, then by induction we know
$$
m(g(\cap_{i=1}^n O_i)) = \int_{\cap_{i=1}^n O_i}g', ~\forall n > 0.
$$
Let $E = \cap_{i=1}^{\infty}O_i $, then first we have
$$
m(g(E)) = m(g(\cap_{i=1}^{\infty} O_i)) \le m(g(\cap_{i=1}^{n} O_i)) = \int_{\cap_{i=1}^{n} O_i} g', ~\forall n.
$$
The left side of this inequity is independent of $n$, thus
$$
m(g(E)) \le \int_{\cap_{i=1}^{\infty} O_i} g' = \int_{E}g'.
$$
On the other hand, we know
$$
\int_{E} g' \le m(g(E))
$$
by the same arguments. Hence
$$
m(g(E)) = \int_{E}g'.
$$
}
\solution{(iii)}{
In a midterm exam we have proved that a strictly increasing and continuous function maps a null set to a null set, thus $m(g(E)) = 0$. By Theorem 10 we know $g'$ is integrable on $[a, b]$, then 
$$
\int_{E} g' = 0.
$$
}
\solution{(iv)}{
For any measurable subset $A$, by Theorem 11 of Chapter 2, there is a $G_\delta $ set $G \supset A$, and $m(G\setminus A) = 0$. Let $E = G\setminus A$, by (ii) and (iii), we have
$$
m(g(E)) = \int_{E} g', ~m(g(G)) = \int_{G}g'.
$$
Since $E\cap G = \emptyset$, by addivity of measure and integral,
$$
m(g(A)) = m(g(E)) + m(g(G)) = \int_{E\cup G}g' = \int_{A}g'.
$$
}
\solution{(v)}{
Since $\varphi$ is a simple function, assume $\varphi = \sum\limits_{k = 1}^{n}c_k1_{E_k} $. Since $E_k $ are measurable sets, we know $g((a, b)) \cap E_k $ are all measurable. Denote $D_k = g((a, b))\cap E_k $. Since $g$ is strictly increasing and continuous, we know $g^{-1}(D_k)$ is measurable, then by addivity of domain and (iv),
$$
\int_{a}^{b}\varphi(g(x))g'(x)dx = \sum_{k=1}^{n}\int_{g^{-1}(D_k)}c_kg'(x)dx = \sum_{k=1}^{n}c_km(g^{-1}(D_k)) = \int_{c}^{d}c_k1_{g^{-1}(D_k)} = \int_{c}^{d}\varphi(x)dx.
$$
}
\solution{(vi)}{
By Simple Approximation Lemma, for any $\epsilon > 0$, there are simple functions $\varphi$ and $\psi$, s.t. 
$$
0 \le \varphi \le f \le \psi, ~0\le\psi-\varphi < \epsilon.
$$
Since $g$ is strictly increasing and absolutely continuous, $g'$ exists a.e., integrable on $[a, b]$, and $g' > 0$. Then
$$
\int_a^b \varphi(g(x))g'(x)dx \le \int_a^b f(g(x))g'(x)dx \le \int_a^b\psi(g(x))g'(x)dx.
$$
By (v) we know
$$
\int_c^d \varphi(y)dy \le \int_a^b f(g(x))g'(x)dx \le \int_c^d \psi(y)dy,
$$
and by montonicity of integrals,
$$
\int_c^d \varphi(y)dy \le \int_c^d f(y)dy \le \int_c^d \psi(y)dy,
$$
and
$$
\int_c^d\psi(y)dy - \int_c^d\varphi(y)dy = \int_c^d(\psi - \varphi)dy \le \epsilon(d-c).
$$
By the arbitrariness of $\epsilon$,
$$
\int_c^d\psi(y)dy - \int_c^d\varphi(y)dy = 0.
$$
Hence
$$
\int_a^b f(g(x))g'(x)dx = \int_c^d f(y)dy.
$$
}

\problem{6}{Problem 59, Page 129}
\solution{Sol}{

@@
